### 2021-11-09 article/article.tex
Paper torture comments

	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.

@@

	Third, our system (and similar spin systems) can be very oscillatory.
	In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz.
	Standard integration methods require very small time-steps in order to accurately depict these oscillations.
	For this reason we use a fourth order Magnus expansion~\cite{magnus_exponential_1954,blanes_magnus_2009} based solver for our geometric integrator to make larger time-steps accurate (see \emph{\nameref{sec:magnus}}).
	We also use a dynamically changing rotating frame to slow down the effective rotations in the system, and thus reduce the size of integration steps being done, making each step more accurate (see \emph{\nameref{sec:rotating_frame}}).

@@

	\subsection{Recent literature}
		While we benchmark \emph{Spinsim} only against industry standard integrators, we also note that application specific quantum numerical simulator packages are regularly being released.
		However, none of these packages are designed specific to quantum sensing, and so these releases are not suitable for simulations highly accurate at high time resolutions required in that field.

@@

	\subsection{Use potential and limitations}
		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.
		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
		While this is viable for some areas of physics research, when designing quantum sensing protocols, we need to take all effects of the spin system and surrounding lab environment into account.
		Thus, \emph{Spinsim}'s primary use is to fill in this gap of simulators for use of developing new quantum sensing protocols with spin-half and spin-one systems, and so should be useful to many within the field of quantum sensing.
		Moreover, \emph{Spinsim} is fast and accurate enough that there is no need to simplify the problem to compromise accuracy for speed.

@@

		So far, the package has also been used to produce simulations for four other new and conceptually distinct quantum sensing protocols from members of the Monash University School of Physics \& Astronomy spinor BEC lab.
		Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available.

@@

		The \emph{Spinsim} package is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only, meaning it is only accurate for the duration that the physical spin system is coherent.
		While ultracold atoms can be coherent for tens of seconds, to the point where decoherence is negligible for most quantum sensing experiments, NVCs have a much shorter coherence time of up to $ 1\,\text{ms} $~\cite{degen_quantum_2017}, so fewer simulations are accurate while ignoring decoherence.
		Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example.

>>>>

	First, while the execution time for these solvers is acceptable for running a small number of experiments, for certain experiments involving large arrays of independent atom clouds (which require many thousands of simulations to be run), this time accumulates to the order of many hours, or even multiple days.
	Given the recent boom in machine learning, many research computers are now equipped with modern graphics processing units (GPUs).
	Their many cores, which can range from hundreds to tens of thousands in number, allows them to run some highly parallel algorithms much faster than a central processing unit (CPU).
	Examples include calculating color values for many pixels on a screen in the titular graphics processing, or the weights in a large neural network.
	While there do exists parallelized algorithms to solve general differential equations~\cite{lions_resolution_2001}, there are properties specific to the spin system that allow for much more fast and elegant parallelization in our use-case.
	We use these properties (see \emph{\nameref{sec:parallelization}}) to write a parallel, GPU based solver that runs faster than industry standard non-parallel algorithms by three orders of magnitude.
	% Mention GPU in fewer words

@@

	Third, our system (and similar spin systems) can be very oscillatory.
	In standard conditions for our application, the expected spin projection of a system that we want to solve for can rotate in physical space (alternatively viewed as a point rotating around an abstract object known as a \emph{Bloch sphere}) at a rate of 700kHz. % Too specific
	Standard integration methods require very small time-steps in order to accurately depict these oscillations.
	For this reason we use a fourth order Magnus expansion~\cite{magnus_exponential_1954,blanes_magnus_2009} based solver for our geometric integrator to make larger time-steps accurate (see \emph{\nameref{sec:magnus}}).
	We also use a dynamically changing rotating frame to slow down the effective rotations in the system, and thus reduce the size of integration steps being done, making each step more accurate (see \emph{\nameref{sec:rotating_frame}}).

@@

	\subsection{Recent literature} % Recent relevant software? Recent software with similar functionality
		While we benchmark \emph{Spinsim} only against industry standard integrators, we also note that application specific quantum numerical simulator packages are regularly being released.
		However, none of these packages are designed specific to quantum sensing, and so these releases are not suitable for simulations highly accurate at high time resolutions required in that field.

@@

	\subsection{Applications}
		The \emph{Spinsim} package will be useful for any research group needing quick, accurate, and/or large numbers of simulations involving spin-half or spin-one systems.
		In particular, the package can simulate a system with complicated (ie not just hard pulses), analytic driving fields, with no approximations like the RWA required, at a high time resolution.% Frequency, amplitude and phase modulation; multiple tones; narrow-band interference; Radiation in control Hamiltonian; interesting polarisation
		We stress that many application specific simulators are designed for the paradigm of using the RWA and/or hard pulse approximations~\cite{suzuki_qulacs_2021, teske_qopt_2021, isakov_simulations_2021}, which both sacrifice accuracy for the sake of speed.
		While this is viable for some areas of physics research, when designing quantum sensing protocols, we need to take all effects of the spin system and surrounding lab environment into account.
		Thus, \emph{Spinsim}'s primary use is to fill in this gap of simulators for use of developing new quantum sensing protocols with spin-half and spin-one systems, and so should be useful to many within the field of quantum sensing.
		Moreover, \emph{Spinsim} is fast and accurate enough that there is no need to simplify the problem to compromise accuracy for speed.

@@

		So far, the package has also been used to produce simulations for four other new and conceptually distinct quantum sensing protocols from members of the Monash University School of Physics \& Astronomy spinor BEC lab.
		Included in this were some honors projects, where \emph{Spinsim} allowed for many quick simulations in the limited time available. % People who have not used quantum computation before have managed to do this

@@

		The \emph{Spinsim} package is designed to simulate small dimensional quantum systems, including large arrays of non-interacting spin systems.
		This means that it would not be able to integrate large arrays of entangled states or interacting particles.
		As a result, despite being fast at simulating qubits, it is inappropriate for the package to be used for quantum computing.
		In addition, \emph{Spinsim} is currently designed to integrate the time evolution of pure states only, meaning it is only accurate for the duration that the physical spin system is coherent.
		While ultracold atoms can be coherent for tens of seconds, to the point where decoherence is negligible for most quantum sensing experiments, NVCs have a much shorter coherence time of up to $ 1\,\text{ms} $~\cite{degen_quantum_2017}, so fewer simulations are accurate while ignoring decoherence.
		Not being able to model decoherence also means that \emph{Spinsim} may not be adequate for use in some nuclear magnetic resonance (NMR) applications where relaxation is important, such as those covered by \emph{SpinEvolution}~\cite{veshtort_spinevolution_2006}, for example. % Too much negativity; Long and adiabatic pulse sequences; simulate in the lab frame, end up with bloch-seigert shifts; targeted at individual quanta, separate regime
